### 2020-04-21 final_report/results.tex
nicer, more realistic results of the first experiment; remove old placeholder plots

The results displayed in~\cref{fig:time-vs-reg} indicate that in the first
experiment, gradient boosted trees clearly appear to be the most accurate as
well as the fastest surrogate class in terms of mean prediction time. Following
that, we note that extremely randomised trees, support vector machines and
neural networks also achieved satisfactory results in both examined metrics.
While the remainder of tested surrogate classes does not exhibit problems in
complexity, its regression performance falls below average.

% TODO: multislice description

\begin{figure}[h]
	\centering
	\begin{subfigure}[b]{0.5\textwidth}
		\centering
		\includegraphics[width=\linewidth]{exp1_time_vs_reg}
		% TODO: only a placeholder, regenerate when data becomes available
		\caption{Experiment 1 (single slice)}
	\end{subfigure}\hfill%
	\begin{subfigure}[b]{0.5\textwidth}
		\centering
		\includegraphics[width=\linewidth]{exp1_time_vs_reg}
		% TODO: only a placeholder, regenerate when data becomes available
		\caption{Experiment 2 (full dataset)}
	\end{subfigure}
	\caption{Regression performance (as $R^2$) plotted against mean
	prediction time for the best $N$~models of each surrogate class.} % TODO. fill N
	\label{fig:time-vs-reg}
\end{figure}

>>>>

The results displayed in~\cref{fig:exp1-time-vs-reg} indicate that in the first
experiment, gradient boosted trees clearly appear to be the most accurate as
well as the fastest surrogate class in terms of mean prediction time. Following
that, we note that extremely randomised trees, support vector machines and
neural networks also achieved satisfactory results in both examined metrics.
While the remainder of tested surrogate classes does not exhibit problems in
complexity, its regression performance falls below average.

\begin{figure}[h]
	\centering
	\begin{subfigure}[b]{0.333\textwidth}
		\centering
		\includegraphics[width=\linewidth]{exp1_slice0}
		% TODO: only a placeholder, regenerate when data becomes available
		\caption{Run 2, batches 0-3}
	\end{subfigure}\hfill%
	\begin{subfigure}[b]{0.333\textwidth}
		\centering
		\includegraphics[width=\linewidth]{exp1_slice1}
		% TODO: only a placeholder, regenerate when data becomes available
		\caption{Run 2, batches 100-103}
	\end{subfigure}\hfill%
	\begin{subfigure}[b]{0.333\textwidth}
		\centering
		\includegraphics[width=\linewidth]{exp1_slice2}
		% TODO: only a placeholder, regenerate when data becomes available
		\caption{Run 2, batches 200-203}
	\end{subfigure}
	\caption{20~best-performing surrogates per each considered class, plotted in
	terms of mean prediction time and regression performance (as~$R^2$) on
	selected slices of run~2, evaluated in experiment~1.}
	\label{fig:exp1-time-vs-reg}
\end{figure}

\begin{wrapfigure}{r}{0.333\textwidth}
	\centering
	\vspace{-3ex}
	\includegraphics[width=\linewidth]{exp2_time_vs_reg}
	% TODO: only a placeholder, regenerate when data becomes available
	\caption{Results of experiment~2, plotted analogously
	to~\cref{fig:exp1-time-vs-reg}.}
	\label{fig:exp2-time-vs-reg}
\end{wrapfigure}

% TODO: multislice description
TODO: multislice description
